P-Threads strikes back

### 2017-07-21 seps-omp-paper.tex
Migrating to ACM sigplan format

\begin{document}
%---
\title{OpenMP is Not as Easy as It Appears, \\
      but It is the Easiest One}
%---
\author{
    \IEEEauthorblockN{Pedro Bruel\IEEEauthorrefmark{1},
                      Paulo Meirelles\IEEEauthorrefmark{1} and
                      Alfredo Goldman\IEEEauthorrefmark{1}}
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Software Systems Laboratory -- LSS\\
    Institute of Mathematics and Statistics -- IME\\
    University of São Paulo -- USP\\
    São Paulo/SP, Brazil\\
    \{phrb,paulormm,gold\}@ime.usp.br}
}
%---
\maketitle
%---
\input{sections/00-abstract}
%---
\IEEEpeerreviewmaketitle
%---
\input{sections/01-introduction}
\input{sections/02-background}
\input{sections/03-relatedwork}
\input{sections/04-researchdesign}
\input{sections/05-dataanalysis}
\input{sections/06-lessons}
\input{sections/07-conclusions}
%---
\input{sections/acknowledgments}
%---
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,seps-omp-paper}
\end{document}

>>>>

\begin{document}
%---
\title{P-Threads strikes back}
%\titlenote{...}
\subtitle{OpenMP is Not as Useful as It Appers}
%\subtitlenote{...}
%---
\author{Pedro Bruel}
%\authornote{This author is the one who did all the really hard work.}
\affiliation{%
  \institution{Software Systems Laboratory (LSS)\\ Institute of Mathematics and Statistics\\ University of São Paulo}
  \streetaddress{Rua do Matão, 1010}
  \city{São Paulo} 
  \country{Brazil}
  \postcode{05508-090}
}
\email{phrb@ime.usp.br}
%---
\author{Paulo Meirelles}
%\authornote{Posdoc}
\affiliation{%
  \institution{FLOSS Competence Center (CCSL)\\ Institute of Mathematics and Statistics\\ University of São Paulo}
  \streetaddress{Rua do Matão, 1010}
  \city{São Paulo} 
  \country{Brazil}
  \postcode{05508-090}
}
\email{paulormm@ime.usp.br}
%---
\author{Alfredo Goldman}
%\authornote{Professor: the head.}
\affiliation{%
  \institution{Software Systems Laboratory (LSS)\\ Institute of Mathematics and Statistics\\ University of São Paulo}
  \streetaddress{Rua do Matão, 1010}
  \city{São Paulo} 
  \country{Brazil}
  \postcode{05508-090}
}
\email{gold@ime.usp.br}

%---

\renewcommand{\shortauthors}{Bruel et al.}

%--
\input{sections/00-abstract}
%---

\maketitle

%---
\input{sections/01-introduction}
\input{sections/02-background}
\input{sections/03-relatedwork}
\input{sections/04-researchdesign}
\input{sections/05-dataanalysis}
\input{sections/06-lessons}
\input{sections/07-conclusions}
%---
\input{sections/acknowledgments}
%---

\bibliographystyle{ACM-Reference-Format}
\bibliography{seps-omp-paper}

\end{document}
